---
title: "Eating Out"
author: "Ashley Davis"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

Is there a difference between races in terms of how often they go out to eat?

There were two years in which the General Social Survey asked about the frequency of eating out.

Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job.

$H_0$ There is no difference among the various races with frequency of eating out per week
$H_A$ There is a statistical difference between at least two races with the frequency of eating out per week  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, include=F}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Method

The variable of the study is Cat ~ Num: Race ~ Eatout

# Results

## Descriptive Results

### Graphical Descriptive Results


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata,type="percent")
```


These bar charts suggest that there is a greater percentage of whites that eat out than black or other races.

### Numerical Descriptive Results

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
The results in this table describe the increased frequency in which whites eat out among the black and other races.

## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll=T)
```
The Chi-Squared Test shows the P-Value as 0.001208. Considering the insignificance of this value, there is a difference in the frequency of how often different races eat out on a weekly basis.

Fisher's Exact Test for count data demonstrates that there is a true difference among the races and how they frequent eating out.


# Discussion and Conclusion

Based on the insignificance of the P-Value, I reject the $H_0$ that states that there is no difference among the various races with frequency of eating out per week, as there is too small of difference for invalidation.

I conclude that therefore there is a statistical difference between at least two races with the frequency of eating out.